\Large Analyzing the Supreme Court Citation Network

### 2018-01-02 Tex/paper.tex
revising citation lit section

Researchers from several fields have used network analysis to analyze citations---legal, patent, and scientific. Before describing the network model for Supreme Court citations that we develop, we review the methods researchers have previously used to study citations.. A citation is a directed link between two documents that indicates the citing document attributes the cited to be in some manner relevant to it. Collective patterns of citations within a certain domain make up citation networks, which are most commonly found in three social systems, scientific publishing, patents, and the judicial system. When raw citation data is formally represented as a network, the nodes are usually the documents themselves, and each directed arc, usually unweighted, is the existence of one or more cites from the sending to the receiving document. Given the permanent nature of documents in citations networks, these networks are in large acyclic \citep{leicht2007large,karrer2009random}. Relatedly, citation networks grow as new documents and citations enter the network, but established arcs persist in all but exceptional cases.

	In its raw form a citation is a link between two documents, but it is the result of human judgment about the utility of the cite \citep{fowler2008authority}. Studies of citation networks can be broadly categorized according to whether they treat this set of observed behavioural patterns as information that can be used to understand different aspects of the system, or treat them as outcomes to be modeled. We discuss these in turn.

>>>>

Researchers from several fields have used network analysis to analyze citations---legal, patent, and scientific. Before describing our approach to modeling the Supreme Court citations, we review the methods researchers have previously used to study citations. A citation is a directed link between two documents that indicates the citing document attributes the cited to be relevant to the evidentiary basis of the citing document. Collective patterns of citations within a certain domain make up citation networks. When raw citation data is formally represented as a network, the nodes are usually the documents themselves, and each directed arc is the existence of one or more cites from the sending to the receiving document. Given the permanent nature of documents in citations networks, these networks are acyclic \citep{leicht2007large,karrer2009random}. Relatedly, citation networks grow as new documents and citations enter the network, but established arcs persist in all but exceptional cases.

	In its raw form a citation is a link between two documents, but it is the result of human judgment about the utility of the cite \citep{fowler2008authority}. Studies of citation networks can be broadly categorized according to whether they treat this set of observed behavioral patterns as information that can be used to understand different aspects of the system, or treat them as outcomes to be modeled. We discuss these in turn.
